probKanren: A Simple Probabilistic extension for microKanren

### 2021-09-14 paper/main.tex
Fix description of program
Add more on microkanren

This probKanren program draws 1000 samples from a normal distribution truncated
below 0.

@@

@@

If we imagine running this program each execution trace can be seen as
a sample from the distribution. If we then weight by their likelihood
as we run them that collection execution traces will be an empirical
distribution of the given program. We call each of these execution traces
particles and the below method is how we obtain them along with their weights $w$.

>>>>

This probKanren program draws 1000 samples from a conditional normal distribution.

@@

Goal expressions represent a possibly backtracking search
procedure. These goals all take as input some state and output a
stream of possible output states. We run these goals by starting with
an initial state that holds an empty substitution dictionary, and
passing it into the top-level goal expression which then passes it
recursively down to sub-expressions. Encountering \texttt{fresh} adds
a new logical variable to the substitution; \texttt{conj} will apply
the first goal to the state passed in, and then apply the second goal
to the states associated with each resulting steam finally unioning
the results; \texttt{disj} will apply both goals to the same passed in
state and concatenate the resulting steam; and \texttt{==} unifies its
arguments in the context of the current state discarding any streams
which fail to unify.

To handle goal expressions that might diverge, the streams are
expanded in an interleaving\cite{kiselyov2005backtracking} fashion
giving each branch a chance to produce answers. This interleaving search
is sound and complete\cite{rozplokhas2019certified}.

@@

If we imagine running this program each execution trace can be seen as
a sample from the distribution. If we then weigh by their likelihood
as we run them that collection of execution traces will be an empirical
distribution of the given program. We call each of these execution traces
particles and the below method is how we obtain them along with their weights $w$.
